---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
library(tidyverse)
library(dplyr)
```


```{r}
warnings <- read_csv('warnings.csv')
rdu <- read_csv('weather_station_data_20220915/rdu_station_data.csv')
# eco <- read_csv('weather_station_data_20220915/econet_weather_station_data.csv')
# roxboro
# tdf <- read_csv('weather_station_data_20220915/tdf_station_data.csv') 
```

```{r date-process}
# get year, month, day from date 
rdut <- rdu
rdut$date <- lubridate::mdy(rdut$date)

rdut %>%
  mutate(year = factor(lubridate::year(date)),
         month = factor(lubridate::month(date)), 
         day = factor(lubridate::day(date))) %>%
  mutate(round_time = hms::as_hms(format(lubridate::floor_date(as.POSIXct(time), unit='hour'), format = "%H:%M:%S")))-> rdut

# MAKES RDUT DF
```

```{r}
# add extreme heat condition var 
warnings %>%
  filter(ph_name %in% c('Excessive Heat', 'Heat' )) %>%
  select(issued, expired, name) %>%
  mutate(issued = lubridate::floor_date(issued, unit = "hour"),
         expired = lubridate::ceiling_date(expired, unit = "hour"),
         diff = as.integer(expired - issued))  -> warnings_c


# where it's negative switch issued and expired 
warnings_c %>%
  filter(diff < 0 ) %>%
  rename(expired = issued, issued = expired) %>%
  mutate(diff = as.integer(expired - issued)) -> warnings_neg

# join 
warnings_fix <- rbind(warnings_c[warnings_c$diff >= 0,], warnings_neg)

# get day month year hour 
warnings_dates <- data.frame()

for (i in 1:nrow(warnings_fix)){
  x <- warnings_fix[i,]
  num <- x$diff
  num1 <- num + 1
  date_i <- rep(x$issued + 3600 * 0:num)
  warnings_i <- rep(x$name, num1)

  df_i <- data.frame(date_i, warnings_i)
  names(df_i) <- c('date', 'name')

  warnings_dates <- rbind(warnings_dates, df_i)
}

# check warnings dates row num 
# sum(warnings_fix$diff) + 36

# make is heat bool var
warnings_dates %>% 
  mutate(is_heat = TRUE, 
         time = hms::as_hms(format(as.POSIXct(date), format = "%H:%M:%S")), 
         date = lubridate::date(date)) -> warnings_dates
```


```{r}
# join warnings and rdu data 
left_join(rdut, warnings_dates, by=c('date', 'round_time'='time')) -> rduw
```

summary stats 

density by factor 


```{r}
# there are no extreme danger points 

# histogram by each variable overall 
rdut %>%
  select(wbgt:hi, year, month, day)%>%
  pivot_longer(cols=wbgt:hi, names_to='type', values_to = 'value') %>%
  ggplot(aes(x = value)) +
  geom_density() +
  facet_wrap(~type, nrow=4, scales='free')+ 
  theme_bw()
  
```

density by month for summer


```{r}
rdut %>%
  select(wbgt:hi, year, month, day) %>%
  filter(month %in% c(5,6,7,8,9)) %>%
  pivot_longer(cols=wbgt:hi, names_to='type', values_to = 'value') %>%
  ggplot(aes(x = value, color = month)) +
  geom_density() +
  facet_wrap(~type, nrow=4, scales='free') + 
  theme_bw()
```

```{r}
rdut %>%
  select(wbgt:hi, year, month, day) %>%
  filter(month %in% c(5,6,7,8,9)) %>%
  pivot_longer(cols=wbgt:hi, names_to='type', values_to = 'value') %>%
  ggplot(aes(x = value, fill = month)) +
  geom_boxplot() +
  facet_wrap(~type, nrow=4, scales='free') +
  theme_bw() 
```

density by year for summer 


```{r}
rdut %>%
  select(wbgt:hi, year, month, day) %>%
  filter(month %in% c(5,6,7,8,9),
         year %in% c(2018, 2019, 2020,2021)) %>%
  pivot_longer(cols=wbgt:hi, names_to='type', values_to = 'value') %>%
  ggplot(aes(x = value, color = year)) +
  geom_density() +
  facet_wrap(~type, nrow=4, scales='free') +
  theme_bw() 
```
```{r}
rdut %>%
  select(wbgt:hi, year, month, day) %>%
  filter(month %in% c(5,6,7,8,9),
         year %in% c(2018, 2019, 2020,2021)) %>%
  pivot_longer(cols=wbgt:hi, names_to='type', values_to = 'value') %>%
  ggplot(aes(x = value, fill = year)) +
  geom_boxplot() +
  facet_wrap(~type, nrow=4, scales='free') +
  theme_bw() 
```

distribution of factor by time of day for summer months


```{r fig.width=10, fig.height=8}
rdut$time2 <- as.character(rdut$time)
rdut %>%
  mutate(hour = as.factor(str_sub(time2, 1,2))) %>%
  select(wbgt:hi, year, month, day, hour) %>%
  filter(month %in% c(5,6,7,8,9)) %>%
  pivot_longer(cols=wbgt:hi, names_to='type', values_to = 'value') %>%
  ggplot(aes(x = value, fill = hour)) +
  geom_boxplot() +
  facet_wrap(~type, nrow=4, scales='free') +
  theme_bw() 

```

```{r}
# make heat warning boolean variable 
# rdut %>%
#   mutate(is_eh = ifelse(eh == 'None', FALSE, TRUE)) -> rdut
# 
# rdut %>% 
#   mutate(is_eh_day = ifelse(date %in% eh_dates$date, TRUE, FALSE)) -> rdut

rduw %>%
  mutate(is_heat = ifelse(is.na(is_heat), FALSE, is_heat),
         is_heat_day = ifelse(date %in% unique(rduw$date[rduw$is_heat == TRUE]), TRUE, FALSE)) -> rduw
```

compare heat warning vs not for each factor 


```{r}
rduw %>%
  filter(month %in% c(5,6,7,8,9)) %>%
  select(wbgt:hi, is_heat) %>%
  pivot_longer(cols=wbgt:hi, names_to='type', values_to = 'value') %>%
  ggplot(aes(x = value, color = is_heat)) +
  geom_density() +
  facet_wrap(~type, nrow=4, scales='free') +
  theme_bw() 
  
```

```{r}
rduw %>%
  filter(month %in% c(5,6,7,8,9)) %>%
  select(wbgt:hi, is_heat) %>%
  pivot_longer(cols=wbgt:hi, names_to='type', values_to = 'value') %>%
  ggplot(aes(x = value, color = is_heat)) +
  geom_boxplot() +
  facet_wrap(~type, nrow=4, scales='free') +
  theme_bw() +
  labs(color = 'Heat Index Warning')
```

```{r}
rduw$day <- factor(rduw$day, levels=c(1:31))
```

```{r}
rduw %>% 
  filter(month %in% c(6,7,8,9)) %>%
  mutate(hour = as.factor(str_sub(time, 1,2))) %>%
  mutate(tod = case_when(
    hour %in% c('22', '23', '00', '01', '02', '03', '04', '05') ~ 'Evening',
    hour %in% c('06', '07', '08', '09', '10', '11') ~ 'Morning',
    hour %in% c('12', '13','14','15','16','17') ~ 'Afternoon',
    hour %in% c('18','19','20','21') ~ 'Early Evening'
  )) -> rdut_tod


rduw %>%
  filter(is_heat_day == TRUE) %>%
  distinct(month, year) -> heat_months

rdut_tod_heat_months <- right_join(rdut_tod, heat_months, by=c('month','year'))

rdut_tod_heat_months$tod <- factor(rdut_tod_heat_months$tod, levels = c('Morning', 'Afternoon', 'Early Evening', 'Evening'))
```

Taking only the month/years in heat warnings occurred: 
Comparing distributions of factors for heat warning vs not by TOD 


```{r}
# comparing true and false by tod by factor for each month 
rdut_tod_heat_months %>%
  ggplot(aes(x =wbgt, fill = is_heat_day)) +
  geom_histogram() + 
  facet_wrap(~tod, scales='free')

rdut_tod_heat_months %>%
  ggplot(aes(x =  ta, fill = is_heat_day)) +
  geom_histogram() + 
  facet_wrap(~tod, scales='free')

rdut_tod_heat_months %>%
  ggplot(aes(x =  rh, fill = is_heat_day)) +
  geom_histogram() + 
  facet_wrap(~tod, scales='free')

rdut_tod_heat_months %>%
  ggplot(aes(x =  td, fill = is_heat_day)) +
  geom_histogram() + 
  facet_wrap(~tod, scales='free')

rdut_tod_heat_months %>%
  ggplot(aes(x =  speed2m, fill = is_heat_day)) +
  geom_histogram() + 
  facet_wrap(~tod, scales='free')

rdut_tod_heat_months %>%
  ggplot(aes(x =  solar, fill = is_heat_day)) +
  geom_histogram() + 
  facet_wrap(~tod, scales='free')

rdut_tod_heat_months%>%
  ggplot(aes(x =  cloudcover, fill = is_heat_day)) +
  geom_histogram() + 
  facet_wrap(~tod, scales='free')

rdut_tod_heat_months %>%
  ggplot(aes(x =  hi, fill = is_heat_day)) +
  geom_histogram() + 
  facet_wrap(~tod, scales='free')

```


look at lag 


```{r}
# rdut %>%
#   distinct(date) -> dates

rduw %>% 
  filter(is_heat_day == TRUE & month %in% c(5,6,7,8,9)) %>%
  distinct(date) -> heat_dates

lag_dates <- data.frame(date = rep(heat_dates$date, each = 6) + -5:0)

# lag_dates <- dates[rep(which(dates$date %in% eh_dates$date), each =6) + -5:0,]

lag_dates$lag <- rep(c('lag5', 'lag4', 'lag3', 'lag2', 'lag1', 'lag0'), times= 37)
lag_dates$indx <- rep(1:37, each = 6)

rduw_lag <- right_join(rduw, lag_dates, by='date')
```


plotting lag 0 vs lag of each one for each factor for each tod 


```{r}
rduw_lag %>%
  select(indx,wbgt, lag, round_time) %>% 
  group_by(indx, lag, round_time) %>%
  summarise(wbgt = mean(wbgt)) %>%
  pivot_wider(names_from=lag, values_from = wbgt) %>%
  pivot_longer(lag1:lag5, names_to='lag', values_to = 'value') %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = value, y = lag0)) +
  geom_point() + 
  geom_smooth() +
  facet_wrap(~lag, scales='free') + 
  labs(x= "WBGT")
  
```

```{r}
rduw_lag %>%
  select(indx,ta, lag, round_time) %>% 
  group_by(indx, lag, round_time) %>%
  summarise(ta = mean(ta)) %>%
  pivot_wider(names_from=lag, values_from = ta) %>%
  pivot_longer(lag1:lag5, names_to='lag', values_to = 'value') %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = value, y = lag0)) +
  geom_point() + 
  geom_smooth(method='lm') +
  facet_wrap(~lag, scales='free') + 
  labs(x= "Air Temp")
```

```{r}
rduw_lag %>%
  select(indx,td, lag, round_time) %>% 
  group_by(indx, lag, round_time) %>%
  summarise(td = mean(td)) %>%
  pivot_wider(names_from=lag, values_from = td) %>%
  pivot_longer(lag1:lag5, names_to='lag', values_to = 'value') %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = value, y = lag0)) +
  geom_point() + 
  facet_wrap(~lag, scales='free') + 
  labs(x= "Dewpoint Temp")
```

```{r}
rduw_lag %>%
  select(indx,solar, lag, round_time) %>% 
  group_by(indx, lag, round_time) %>%
  summarise(solar = mean(solar)) %>%
  pivot_wider(names_from=lag, values_from = solar) %>%
  pivot_longer(lag1:lag5, names_to='lag', values_to = 'value') %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = value, y = lag0)) +
  geom_point() + 
  facet_wrap(~lag, scales='free') + 
  labs(x= "Solar")
```

```{r}
rduw_lag %>%
  select(indx,rh, lag, round_time) %>% 
  group_by(indx, lag, round_time) %>%
  summarise(rh = mean(rh)) %>%
  pivot_wider(names_from=lag, values_from = rh) %>%
  pivot_longer(lag1:lag5, names_to='lag', values_to = 'value') %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = value, y = lag0)) +
  geom_point() + 
  geom_smooth(method='lm') +
  facet_wrap(~lag, scales='free') + 
  labs(x= "Relative Humidity")
```

```{r}
rduw_lag %>%
  select(indx,hi, lag, round_time) %>% 
  group_by(indx, lag, round_time) %>%
  summarise(hi = mean(hi)) %>%
  pivot_wider(names_from=lag, values_from = hi) %>%
  pivot_longer(lag1:lag5, names_to='lag', values_to = 'value') %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = value, y = lag0)) +
  geom_point() + 
  geom_smooth(method='lm') +
  facet_wrap(~lag, scales='free') + 
  labs(x= "Heat Index")
```

```{r}
rduw_lag %>%
  select(indx,speed2m , lag, round_time) %>% 
  group_by(indx, lag, round_time) %>%
  summarise(speed2m= mean(speed2m)) %>%
  pivot_wider(names_from=lag, values_from = speed2m) %>%
  pivot_longer(lag1:lag5, names_to='lag', values_to = 'value') %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = value, y = lag0)) +
  geom_point() + 
  facet_wrap(~lag, scales='free') + 
  labs(x= "Wind Speed")
```

```{r}
rduw_lag %>%
  select(indx,cloudcover , lag, round_time) %>% 
  group_by(indx, lag, round_time) %>%
  summarise(cloudcover= mean(cloudcover)) %>%
  pivot_wider(names_from=lag, values_from = cloudcover) %>%
  pivot_longer(lag1:lag5, names_to='lag', values_to = 'value') %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = value, y = lag0)) +
  geom_point() + 
  geom_jitter() + 
  facet_wrap(~lag, scales='free') + 
  labs(x= "Cloud")
```

```{r}
rduw_lag %>%
  filter(lag == 'lag0') %>%
  select(wbgt, round_time, indx)%>%
  rename(lag0 = wbgt)-> wbgt_lag0

rduw_lag %>%
  filter(lag == 'lag1') %>%
  select(is_heat_day, wbgt, indx, round_time) %>%
  rename(lag1 = wbgt) %>%
  left_join(wbgt_lag0, by = c('indx', 'round_time')) %>%
  ggplot(aes(x = lag1, y = lag0, color = is_heat_day)) +
  geom_point() 
```

```{r}
rduw_lag %>%
  filter(lag == 'lag0') %>%
  select(td, round_time, indx)%>%
  rename(lag0 = td)-> lag0

rduw_lag %>%
  filter(lag == 'lag1') %>%
  select(is_heat_day, td, indx, round_time) %>%
  rename(lag1 = td) %>%
  left_join(lag0, by = c('indx', 'round_time')) %>%
  ggplot(aes(x = lag1, y = lag0, color = is_heat_day)) +
  geom_point()
```

```{r}
# lag 1 2 3  of all days for the months that heat index occurs 

rduw %>%
  filter(is_heat_day == TRUE) %>%
  distinct(month, year) -> heat_months

rduw_heat_months <- right_join(rduw, heat_months, by=c('month','year'))

lag_dates_all <- data.frame(date = rep(unique(rduw_heat_months$date), each = 3) + -2:0)

lag_dates_all$lag <- rep(c('lag2', 'lag1', 'lag0'), times= nrow(lag_dates_all) /3)
lag_dates_all$indx <- rep(1:(nrow(lag_dates_all)/3), each = 3)

rduw_lag_all <- right_join(rduw, lag_dates_all, by='date')
```

```{r}
# check lag days vs none  
rduw_lag_all$is_heat_day <- factor(rduw_lag_all$is_heat_day, levels=c(TRUE, FALSE))

rduw_lag_all%>%
  filter(lag == 'lag0') %>%
  select(solar, round_time, indx, is_heat_day )%>%
  rename(lag0 = solar)-> lag0

rduw_lag_all %>%
  filter(lag == 'lag1') %>%
  select(is_heat_day, solar, indx, round_time) %>%
  rename(lag1 = solar) %>%
  full_join(lag0, by = c('indx', 'round_time', 'is_heat_day'))  %>%
  filter(!is.na(is_heat_day) & !is.na(lag0) & !is.na(lag1)) -> rduw_lag_solar 

rduw_lag_solar %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x = lag1, y = lag0, color = is_heat_day)) +
  geom_point() + 
  labs(title='Solar') + 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_all%>%
  filter(lag == 'lag0') %>%
  select(speed2m, round_time, indx, is_heat_day )%>%
  rename(lag0 = speed2m)-> lag0

rduw_lag_all %>%
  filter(lag == 'lag1') %>%
  select(is_heat_day, speed2m, indx, round_time) %>%
  rename(lag1 = speed2m) %>%
  full_join(lag0, by = c('indx', 'round_time', 'is_heat_day'))  %>%
  filter(!is.na(is_heat_day) & !is.na(lag0) & !is.na(lag1)) -> rduw_lag_ws

rduw_lag_ws %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x = lag1, y = lag0, color = is_heat_day)) +
  # geom_smooth()+ 
  geom_point() +
  labs(title='Wind Speed') + 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_all%>%
  filter(lag == 'lag0') %>%
  select(ta, round_time, indx, is_heat_day )%>%
  rename(lag0 = ta)-> lag0

rduw_lag_all %>%
  filter(lag == 'lag1') %>%
  select(is_heat_day, ta, indx, round_time) %>%
  rename(lag1 = ta) %>%
  full_join(lag0, by = c('indx', 'round_time', 'is_heat_day'))  %>%
  filter(!is.na(is_heat_day) & !is.na(lag0) & !is.na(lag1)) -> rduw_lag_ta

rduw_lag_ta %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x = lag1, y = lag0, color = is_heat_day)) +
  # geom_smooth() + 
  geom_point() +
  labs(title='Air Temp') + 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_all%>%
  filter(lag == 'lag0') %>%
  select(td, round_time, indx, is_heat_day )%>%
  rename(lag0 = td)-> lag0

rduw_lag_all %>%
  filter(lag == 'lag1') %>%
  select(is_heat_day, td, indx, round_time) %>%
  rename(lag1 = td) %>%
  full_join(lag0, by = c('indx', 'round_time', 'is_heat_day'))  %>%
  filter(!is.na(is_heat_day) & !is.na(lag0) & !is.na(lag1)) -> rduw_lag_td

rduw_lag_td %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x = lag1, y = lag0, color = is_heat_day)) +
  # geom_smooth()+ 
  geom_point() +
  labs(title='Dewpoint Temp') + 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_all%>%
  filter(lag == 'lag0') %>%
  select(hi, round_time, indx, is_heat_day )%>%
  rename(lag0 = hi)-> lag0

rduw_lag_all %>%
  filter(lag == 'lag1') %>%
  select(is_heat_day, hi, indx, round_time) %>%
  rename(lag1 = hi) %>%
  full_join(lag0, by = c('indx', 'round_time', 'is_heat_day'))  %>%
  filter(!is.na(is_heat_day) & !is.na(lag0) & !is.na(lag1)) -> rduw_lag_hi

rduw_lag_hi %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x = lag1, y = lag0, color = is_heat_day)) +
  # geom_smooth()+ 
  geom_point() +
  labs(title='Heat Index') + 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_all%>%
  filter(lag == 'lag0') %>%
  select(rh, round_time, indx, is_heat_day )%>%
  rename(lag0 = rh)-> lag0

rduw_lag_all %>%
  filter(lag == 'lag1') %>%
  select(is_heat_day, rh, indx, round_time) %>%
  rename(lag1 = rh) %>%
  full_join(lag0, by = c('indx', 'round_time', 'is_heat_day'))  %>%
  filter(!is.na(is_heat_day) & !is.na(lag0) & !is.na(lag1)) -> rduw_lag_rh

rduw_lag_rh %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x = lag1, y = lag0, color = is_heat_day)) +
  # geom_smooth()+ 
  geom_point() +
  labs(title='Humidity') + 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_all%>%
  filter(lag == 'lag0') %>%
  select(wbgt, round_time, indx, is_heat_day )%>%
  rename(lag0 = wbgt)-> lag0

rduw_lag_all %>%
  filter(lag == 'lag1') %>%
  select(is_heat_day, wbgt, indx, round_time) %>%
  rename(lag1 = wbgt) %>%
  full_join(lag0, by = c('indx', 'round_time', 'is_heat_day'))  %>%
  filter(!is.na(is_heat_day) & !is.na(lag0) & !is.na(lag1)) -> rduw_lag_wbgt

rduw_lag_wbgt %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x = lag1, y = lag0, color = is_heat_day)) +
  # geom_smooth()+ 
  geom_point() +
  labs(title='WBGT') + 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))
```

```{r}
# check correlation of points between 0 and none 
corrs_df <- data.frame(rbind(
  c(cor(x=rduw_lag_td$lag0[rduw_lag_td$is_heat_day == TRUE], y=rduw_lag_td$lag1[rduw_lag_td$is_heat_day == TRUE]),
    cor(x=rduw_lag_td$lag0[rduw_lag_td$is_heat_day == FALSE], y=rduw_lag_td$lag1[rduw_lag_td$is_heat_day == FALSE])),
  c(cor(x=rduw_lag_ta$lag0[rduw_lag_ta$is_heat_day == TRUE], y=rduw_lag_ta$lag1[rduw_lag_ta$is_heat_day == TRUE]),
    cor(x=rduw_lag_ta$lag0[rduw_lag_ta$is_heat_day == FALSE], y=rduw_lag_ta$lag1[rduw_lag_ta$is_heat_day == FALSE])),
  c(cor(x=rduw_lag_wbgt$lag0[rduw_lag_wbgt$is_heat_day == TRUE], y=rduw_lag_wbgt$lag1[rduw_lag_wbgt$is_heat_day == TRUE]),
    cor(x=rduw_lag_wbgt$lag0[rduw_lag_wbgt$is_heat_day == FALSE],y=rduw_lag_wbgt$lag1[rduw_lag_wbgt$is_heat_day==FALSE])),
  c(cor(x=rduw_lag_rh$lag0[rduw_lag_rh$is_heat_day == TRUE], y=rduw_lag_rh$lag1[rduw_lag_rh$is_heat_day == TRUE]),
    cor(x=rduw_lag_rh$lag0[rduw_lag_rh$is_heat_day == FALSE], y=rduw_lag_rh$lag1[rduw_lag_rh$is_heat_day == FALSE])),
  c(cor(x=rduw_lag_hi$lag0[rduw_lag_hi$is_heat_day == TRUE], y=rduw_lag_hi$lag1[rduw_lag_hi$is_heat_day == TRUE]),
    cor(x=rduw_lag_hi$lag0[rduw_lag_hi$is_heat_day == FALSE], y=rduw_lag_hi$lag1[rduw_lag_hi$is_heat_day == FALSE])),
  c(cor(x=rduw_lag_solar$lag0[rduw_lag_solar$is_heat_day == TRUE], y=rduw_lag_solar$lag1[rduw_lag_solar$is_heat_day == TRUE]),
    cor(x=rduw_lag_solar$lag0[rduw_lag_solar$is_heat_day == FALSE], y=rduw_lag_solar$lag1[rduw_lag_solar$is_heat_day == FALSE])),
  c(cor(x=rduw_lag_ws$lag0[rduw_lag_ws$is_heat_day == TRUE], y=rduw_lag_ws$lag1[rduw_lag_ws$is_heat_day == TRUE]),
    cor(x=rduw_lag_ws$lag0[rduw_lag_ws$is_heat_day == FALSE], y=rduw_lag_ws$lag1[rduw_lag_ws$is_heat_day == FALSE]))
  ))

names(corrs_df) <- c('Heat Warning', 'No Heat Warning')
row.names(corrs_df) <- c('Dewpoint Temp', 'Air Temp', 'WBGT', 'Humidity', 'Heat Index', 'Solar', 'Wind Speed')

corrs_df
```


```{r}
rduw_lag_solar %>%
  mutate(hour = as.factor(str_sub(round_time, 1,2))) %>%
  mutate(tod = case_when(
    hour %in% c('22', '23', '00', '01', '02', '03', '04', '05') ~ 'Evening',
    hour %in% c('06', '07', '08', '09', '10', '11') ~ 'Morning',
    hour %in% c('12', '13','14','15','16','17') ~ 'Afternoon',
    hour %in% c('18','19','20','21') ~ 'Early Evening'
  )) %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x =  lag1, y= lag0, color = is_heat_day)) +
  geom_point() + 
  # geom_smooth() + 
  facet_wrap(~tod, scales='free') + 
  labs(title='Solar')+ 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_ta %>%
  mutate(hour = as.factor(str_sub(round_time, 1,2))) %>%
  mutate(tod = case_when(
    hour %in% c('22', '23', '00', '01', '02', '03', '04', '05') ~ 'Evening',
    hour %in% c('06', '07', '08', '09', '10', '11') ~ 'Morning',
    hour %in% c('12', '13','14','15','16','17') ~ 'Afternoon',
    hour %in% c('18','19','20','21') ~ 'Early Evening'
  )) %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x =  lag1, y= lag0, color = is_heat_day)) +
  geom_point() + 
  # geom_smooth() + 
  facet_wrap(~tod, scales='free') + 
  labs(title='Air Temp')+ 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_td %>%
  mutate(hour = as.factor(str_sub(round_time, 1,2))) %>%
  mutate(tod = case_when(
    hour %in% c('22', '23', '00', '01', '02', '03', '04', '05') ~ 'Evening',
    hour %in% c('06', '07', '08', '09', '10', '11') ~ 'Morning',
    hour %in% c('12', '13','14','15','16','17') ~ 'Afternoon',
    hour %in% c('18','19','20','21') ~ 'Early Evening'
  )) %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x =  lag1, y= lag0, color = is_heat_day)) +
  geom_point() + 
  # geom_smooth() + 
  facet_wrap(~tod, scales='free') + 
  labs(title='Dewpoint Temp')+ 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_wbgt %>%
  mutate(hour = as.factor(str_sub(round_time, 1,2))) %>%
  mutate(tod = case_when(
    hour %in% c('22', '23', '00', '01', '02', '03', '04', '05') ~ 'Evening',
    hour %in% c('06', '07', '08', '09', '10', '11') ~ 'Morning',
    hour %in% c('12', '13','14','15','16','17') ~ 'Afternoon',
    hour %in% c('18','19','20','21') ~ 'Early Evening'
  )) %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x =  lag1, y= lag0, color = is_heat_day)) +
  geom_point() + 
  # geom_smooth() + 
  facet_wrap(~tod, scales='free') + 
  labs(title='WBGT')+ 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_rh %>%
  mutate(hour = as.factor(str_sub(round_time, 1,2))) %>%
  mutate(tod = case_when(
    hour %in% c('22', '23', '00', '01', '02', '03', '04', '05') ~ 'Evening',
    hour %in% c('06', '07', '08', '09', '10', '11') ~ 'Morning',
    hour %in% c('12', '13','14','15','16','17') ~ 'Afternoon',
    hour %in% c('18','19','20','21') ~ 'Early Evening'
  )) %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x =  lag1, y= lag0, color = is_heat_day)) +
  geom_point() + 
  # geom_smooth() + 
  facet_wrap(~tod, scales='free') + 
  labs(title='Humidity')+ 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_hi %>%
  mutate(hour = as.factor(str_sub(round_time, 1,2))) %>%
  mutate(tod = case_when(
    hour %in% c('22', '23', '00', '01', '02', '03', '04', '05') ~ 'Evening',
    hour %in% c('06', '07', '08', '09', '10', '11') ~ 'Morning',
    hour %in% c('12', '13','14','15','16','17') ~ 'Afternoon',
    hour %in% c('18','19','20','21') ~ 'Early Evening'
  )) %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x =  lag1, y= lag0, color = is_heat_day)) +
  geom_point() + 
  # geom_smooth() + 
  facet_wrap(~tod, scales='free') + 
  labs(title='Heat Index')+ 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))

rduw_lag_ws %>%
  mutate(hour = as.factor(str_sub(round_time, 1,2))) %>%
  mutate(tod = case_when(
    hour %in% c('22', '23', '00', '01', '02', '03', '04', '05') ~ 'Evening',
    hour %in% c('06', '07', '08', '09', '10', '11') ~ 'Morning',
    hour %in% c('12', '13','14','15','16','17') ~ 'Afternoon',
    hour %in% c('18','19','20','21') ~ 'Early Evening'
  )) %>%
  arrange(desc(is_heat_day)) %>%
  ggplot(aes(x =  lag1, y= lag0, color = is_heat_day)) +
  geom_point() + 
  # geom_smooth() + 
  facet_wrap(~tod, scales='free') + 
  labs(title='Wind Speed')+ 
  scale_color_manual(values=c('#3388FF','#D3D3D3'))
# check time of day 
# check evening hours before 
```

















